---
title: "R_Project"
author: "Shuheng.Ma"
date: "8/7/2019"
output: pdf_document
---


```{r}
library(ISLR)
library(glmnet)
library(lattice)
library(ggplot2)
library(caret)
library(Matrix)
library(foreach)
library(pls)
```


# Data clean Part
# SOMEHOW This part of code cannot be put into R-markdown, otherwise will result in error.

rm(list=ls())
setwd('C:/Users/mshch96/Desktop/Predictive Models/R Scripts/R_dir/project')
airbnb = read.csv("listings.csv")
nrow(airbnb)

airbnb <- airbnb[which(airbnb$city=='Austin'),]
attach(airbnb)

int_var_orig <- c('price','accommodates','bathrooms' ,'bedrooms','beds',
                  'guests_included','security_deposit','cleaning_fee')  
int_var <- c('price','accommodates','bathrooms' ,'bedrooms','beds',
             'guests_included','host_response_time','host_is_superhost'
             ,'number_of_reviews','cancellation_policy','maximum_nights','availability_365',
             'availability_30','availability_60','availability_90','neighbourhood_cleansed',
             'host_total_listings_count','host_identity_verified','calculated_host_listings_count',
             'beds','room_type','property_type')
airb <- airbnb[int_var] # 9556
airb <- na.omit(airb) #9506
#summary(airb)
nrow(airb) #9506

attach(airb)

airb$price= as.numeric(gsub("\\$", "", airb$price))
length(airb$price) #9506
summary(airb$price) #415 na 

airb$security_deposit= as.numeric(gsub("\\$", "", airb$security_deposit))
security_deposit
summary(airb$security_deposit) # 5717 missing values, drop! 

airb$cleaning_fee = as.numeric(gsub("\\$", "", airb$cleaning_fee))
airb$cleaning_fee
summary(airb$cleaning_fee) # 3320 missing values, drop! 
host_is_superhost = as.factor(airb$host_is_superhost)
host_is_superhost = ifelse(host_is_superhost=="t",1,0)
length(host_is_superhost)
#airb <- na.omit(airb)

#NA2mean <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))
#replace(cleaning_fee, TRUE, lapply(cleaning_fee, NA2mean))
#lapply(cleaning_fee,NA2mean)
#summary(cleaning_fee)

airb = na.omit(airb) #9091
nrow(airb) #9091
summary(airb)


#install.packages("dplyr")
library(dplyr)
airb=airb %>% filter(airb$price!=0)

lm_accom = lm(price~accommodates) #31% 
summary(lm_accom)

lm_bath = lm(price~bathrooms)
summary(lm_bath)


attach(airb)
length(accommodates) #9090



num_reviews=airb$number_of_reviews
length(num_reviews)

cancel=as.factor(airb$cancellation_policy)
length(cancel)
summary(cancel)

avail_365 = airb$availability_365
length(avail_365)

avail_30 = airb$availability_30
length(avail_30)

avail_60 = airb$availability_60
length(avail_60)

avail_90 = airb$availability_90
length(avail_90)

host_is_superhost = as.factor(airb$host_is_superhost)
host_is_superhost = ifelse(host_is_superhost=="t",1,0)
length(host_is_superhost)

zip = airb$neighbourhood_cleansed
length(zip)
uni_zip=unique(zip)
zip_sort=sort(uni_zip)
zip[zip<78715] <- "zip_one"
zip[78714<zip & zip<78730] <- "zip_two" 
zip[78729<zip & zip<78745] <- "zip_three"
zip[78744<zip & zip<78760] <- "zip_four"
length(zip)
summary(zip)


host_list = airb$calculated_host_listings_count

total_list = airb$host_total_listings_count
length(total_list)

host_id = airb$host_identity_verified

#max_nights = airb$maximum_nights
#length(max_nights)

model = lm(airb$price~accommodates+bathrooms+bedrooms+beds+guests_included+
             host_is_superhost+num_reviews+avail_365+avail_30+avail_60+avail_90+zip+total_list
           +host_id+host_list+room_type)
summary(model)

levels(room_type)


# best subset selection
library(leaps)
sub_select = regsubsets(price~accommodates+bathrooms+bedrooms+beds+guests_included+
                          host_is_superhost+num_reviews+avail_365+avail_30+avail_60+avail_90+zip+total_list
                        +host_id+host_list+room_type,airb) #16 variables 
summary(sub_select)
#accodmodates, bathrooms, bedrooms, super, num_rev, avail_30, avail_90, zip_one, 
# room_type 

red_model = lm(price~accommodates+bathrooms+bedrooms+
                 host_is_superhost+num_reviews+avail_30+avail_90+zip
               +room_type,airb)
summary(red_model) 
nrow(airb)


############################################################################
reg_var <- c('price','accommodates','bathrooms' ,'bedrooms'
             ,'host_is_superhost','number_of_reviews',
             'availability_30','availability_90','neighbourhood_cleansed',
             'room_type')
reg_data <- airb[reg_var]

nrow(reg_data)




```{r}
# Split into train and test

x = model.matrix(price~., reg_data[,-1])
y = reg_data$price
grid =  grid=10^seq(10,-2, length =100)

set.seed(2)
#train=(reg_data[1:8000,])
#test = (reg_data[-(1:8000),])


train = sample(1:nrow(x),nrow(x)/2)
test = (-train)
y.test = y[test]
```

```{r}
#OLS

ls = lm(price~.,data = reg_data, subset = train)
ols.pred = predict(ls, data= test)
error.ols = sqrt(mean((ols.pred -y.test)^2))
error.ols # 244.3186
```





```{r}

# Ridge Reg:
# Initial work

ridge.mod=glmnet(x[train,],y[train],alpha=0,lambda=grid, thresh=1e-12)

# get best lambda:
cv.out = cv.out=cv.glmnet(x[train,],y[train],alpha=0)
plot(cv.out)
bestlam =cv.out$lambda.min  # bestlam= 11.43546
bestlam
# MSE
ridge.pred=predict (ridge.mod ,s=bestlam,newx=x[test ,])
error.ridge = sqrt(mean((ridge.pred -y.test)^2))
error.ridge # 143.096
```


```{r}

# lasso:
lasso.mod=glmnet(x[train,],y[train],alpha=1,lambda=grid)

cv.out=cv.glmnet(x[train,],y[train],alpha=1)
bestlam =cv.out$lambda.min # bestlam = 0.1863695
bestlam

lasso.pred=predict (lasso.mod ,s=bestlam ,newx=x[test,])
error.lasso = sqrt(mean((lasso.pred -y.test)^2)) 
error.lasso
# error = 142.7406

```


```{r}


#pcr:
pcr.fit=pcr(price~., data=reg_data ,subset=train,scale=TRUE, validation="CV")
validationplot(pcr.fit ,val.type="MSEP")
summary (pcr.fit) # M = 6, RMSE = 152          
```


```{r}

# PLS:
pls.fit = plsr(price~.,data = reg_data, subset = train, scale = TRUE, validation = "CV")
validationplot(pls.fit,val.type = "MSEP")
summary(pls.fit) # M = 4, RMSE = 150.9    

coef(pcr.fit)
```

